First exclusive Deeply Virtual Compton Scattering measurement off bound nucleon in $^4$He

### 2018-03-09 eg6-letters/incoherent/incoherent_prl.tex
Corrections to the incoherent letter

%
\begin{document}
\linenumbers

\title{First exclusive DVCS measurement off bound nucleon in $^4$He}
%\title{Revealing the Bound Nucleon 3D Partonic Structure through Incoherent Deeply Virtual Compton Scattering off $^4$He}

@@

%
\date{\today}
\begin{abstract}
We report on the beam-spin asymmetries associated with incoherent deeply 
   virtual Compton scattering off $^4$He in the valence quark region. The data 
   were accumulated using a 6 GeV longitudinally-polarized electron beam 
   incident on a pressurized $^4$He gaseous target placed in front of the CLAS 
   spectrometer in Hall-B at the Thomas Jefferson National Accelerator 
   Facility.  The baseline detection sub-systems of CLAS detected the scattered 
   electrons and the recoil protons, while the final-state real photons are 
   detected by a supplementary electromagnetic calorimeter at very forward 
   angles. The measured beam-spin asymmetries on bound-protons exhibit a 
   suppression compared to those on free proton, indicating possible medium 
   modifications on the nucleon's quark distributions and opening new 
   opportunities to explore the origin of the EMC effect within the framework 
   of the generalized parton distributions.

@@

Electromagnetic probes have played a major role in advancing our knowledge 
about the structure of nucleons, which are the origin of almost all the
Universe's visible matter. While elastic lepton-nucleon measurements have 
taught us about the spatial charge and magnetization distributions 
\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering (DIS) 
experiments have uncovered the features of momentum sharing between the 
constituents partons, i.e., quarks and gluons \cite{Dokshitzer:1977sg,pdg}.  
With nuclear targets, the DIS measurements have revealed the fact that the 
distribution of quarks in a fast moving nucleus is not a simple convolution of 
their distributions within nucleons, an observation known as the ``EMC 
effect''\cite{EMC_first} (for reviews on the extensive investigations, see  
\cite{EMC_CERN,EMC_SLAC,EMC_HERMES,EMC_JLab,EMC_John,EMC_mdeium_1,EMC_medium_2}).

A wealth of information on the structure of matter lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations are set to be revealed through deeply virtual Compton scattering 
(DVCS), i.e., the hard exclusive lepto-production of a real photon, which 
provides access to a three-dimensional imaging of partons within the 
generalized parton distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, HERA and  
CERN. Combining these measurements has enabled the first extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of exclusive DVCS from the $^{4}$He nucleus are a critical 
step towards providing similar 3-D pictures of the quark structure of the 
nucleus as a whole, via the coherent channel 
\cite{Airapetian:2009cga,Hattawy:2017woc}, and provide a new approach for 
understanding modifications of the partonic structure of the bound nucleons via 
the incoherent DVCS channel \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for these purposes as it has 
only one chiral-even GPD that parametrizes its partonic structure, is 
characterized by a strong binding energy, and has a relatively high nuclear 
core density. The inclusive scattering off $^{4}$He has shown a large EMC 
effect \cite{JSeely}, making this nucleus a golden target for investigating the 
medium modifications of the nucleon's partonic structure.

@@

In this Letter, we present the first exclusive measurement of the beam-spin asymmetry in deeply virtual electroproduction of a real photon off bound-proton in $^{4}$He. Experimentally we measure squared sum of the Bethe-Heitler (BH) and DVCS amplitudes, with BH process where real photon is emitted by the incident or the scattered electron dominating the cross section in our kinematics.   
%While the experimentally measured cross section amplitude is the sum of the DVCS, BH (i.e., the final state real photon is emitted by the incident or the scattered electron), and their interference, 
The beam-spin asymmetry, in other hand, is sensitive to the DVCS amplitude and the interference term that contain information on the GPDs. 
The beam-spin asymmetry observable with a longitudinally polarized electron beam (L) and unpolarized target (U) is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the 
beam-spin asymmetry can be simplified as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ 
and is proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   A_{LU}^{\sin\phi} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} 
   F_2 \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors with $x_B$ as the 
Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  
\begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi) \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ is the Cauchy principal value integral and $C^{+}$ is a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$ with $\xi$ being 
related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
for the GPDs $E$, $\widetilde{H}$, and $\widetilde{E}$.

@@

The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
(CEBAF) accelerator at energy of 6.064 GeV. The data were accumulated 
over 40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous 
$^4$He target centered at 64~cm upstream of the CEBAF Large Acceptance 
Spectrometer (CLAS) coordinate center. For similar DVCS experiments on free-proton target
\cite{Girod:2007aa,Jo:2015ema}, the CLAS baseline design \cite{Mecking:2003zu} 
is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC extends 
the photon detection acceptance of CLAS to very small polar angles, 4$^{\circ}$. 
%As the coherent DVCS off $^4$He, where the nucleus remain intact, was one of the proposed measurements of our experiment and since CLAS cannot detect such low-energy recoil nuclei, we built a small radial time projection chamber (RTPC) around the target cell. (See~\cite{Dupre:2017upj} for a detailed description of the RTPC and its performances and \cite{Hattawy:2017woc} for the coherent DVCS measurements). In this setup, 
The 5-Tesla solenoid magnet in the center of which target was located 
%(that surrounds the target and the RTPC) enabled the detection of the low-energy charged ions in the RTPC and 
prevented the high-rate low-energy M{\o}ller electrons from reaching the CLAS drift chambers by guiding them electrons insde a tungsten shield placed around the beam line.

% DVCS selection
Incoherent DVCS events were selected if an electron, a proton, and at least one 
photon were detected in the final state. Electrons were identified as negatively charged tracks reconstructed in drift chambers with an appropriate energy deposition in the electromagnetic calorimeters (EC) and a proper 
light yield in the Cherenkov counters. The protons were identified from positively charged tracks by 
timing analysis using the time-of-flight measured by the scintillator counters. 
In addition, it was required that both the electron and the proton in the event originated from the same vertex at the target within CLAS tracking vertex resolution. The photons were detected in either the IC or 
the CLAS electromagnetic calorimeters. All the clusters within the IC fiducial region 
were assumed to be photons, while a timing cut is used to clean the EC photons 
from neutrons. Note that even though the DVCS reaction has only one real photon 
in the final state, events with more than one photon were not discarded at 
this stage. As will be discussed below, the DVCS exclusivity cuts allow identification of the correct photon in the event, discarding accidental, mostly soft photons. In the following selection stage, the most energetic photon is considered as the DVCS 
photon candidate (see \cite{Hattawy:thesis} for additional details on the particles identification).

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
events due to accidental coincidences and exclusive $\pi^0$ production where one of photons from $\pi^0$ decay escape the detection. For the accidental events, i.e., $e'p'\gamma$ collection 
with particles originated from different electron scattering events, their contribution of 6.5\% 
was evaluated by selecting events passing all our cuts but originating from 
different vertices. The $\pi^0$ contamination 
%, i.e., $ep\rightarrow e'p'\pi^0$ events where one of the two photons of the $\pi^0$ decay is produced below the energy threshold or outside the detection acceptance, we
was estimated 
%this contribution by 
using the data and simulation. From simulation, we 
calculated the ratio ($R$) of the number of $\pi^0$ events that are identified as $ep\rightarrow e'p'\gamma$ events after our selection cuts to the number of identified $\pi^0$ events, $R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
experimentally identified number of $ep\rightarrow e'p'\gamma$ and 
$N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
$ep\rightarrow e'p'\pi^0$ with the two photons were detected. Depending on the 
kinematics, we found contaminations of 8\%-10\%.

%asymmetries
%It is convenient to use the beam-spin asymmetry as a DVCS observable because  the cross sections luminosity normalization and detector efficiencies cancel out in the asymmetry ratio.  
Experimentally, $A_{LU}$ 
%can be simplified in terms of the reaction yield in each beam-helicity state ($N^{\pm}$) 
is defined as
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\end{equation}
where $N^{+}$ and $N^{-}$ are the number of DVCS events for positive and negative  beam-helicity state, and $P_{B}$ is the longitudinal beam polarization.

In the kinematical domain of our experiment, the dominant contribution to the beam-spin asymmetry comes from GPD H \cite{Guidal:2013rya} and
%Following the model guidance of \cite{Guidal:2013rya}, the GPD $H$ dominants the other three GPDs within the accessible phase-phase of using the 6 GeV electron beam from CEBAF and CLAS spectrometer. Therefore, 
therefore $\phi$ dependence of $A_{LU}$ gives access to the real and imaginary part of the CFF $\mathcal{H}$ through 
the parameters $a_0$, $a_1$, and $a_2$ of equation \ref{eq:alu-simp}. The studies of  
the free proton $A_{LU}$ measurements, \cite{Girod:2007aa}, have 
shown that the the pure DVCS contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with zero.

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four statistically-equivalent bins in each of the kinematical 
variables ($Q^{2}$, $x_{B}$, $t$) were constructed one at a time. Then, each 
bin is divided into nine bins in the azimuthal angle ($\phi$).  
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
of the approximated form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The 
study of systematic uncertainties showed that the main contributions come from 
the choice of the DVCS exclusivity cuts (6\%) and the large binning size (7\%).  
Added quadratically, these uncertainties sum up to less than 10\% for all data points and are significantly smaller than the statistical errors.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and 
   $-t$ bins (bottom panel). The error bars represent the statistical 
   uncertainties. The gray bands represent the systematic uncertainties, 
   including the normalisation uncertainties. The black curves are the results 
   of our fits with the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$.}
\label{fig:alu}
\end{figure}

We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
signals at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model uses a realistic spectral function and 
considers off-shell effects. The calculations are carried out at slightly 
different kinematics than our data but still provide important guidance. The 
experimental results appear to have smaller asymmetries than the calculations.  
These differences may arise from nuclear effects which are not taken into 
account in the model, such as long-range interactions. On the graph for $t$ dependence we show previous measurements by  the HERMES collaboration  \cite{Airapetian} using inclusive final state, ($e^\prime\gamma$). Due to large experimental uncertainties of HERMES points, the only conclusion is that the two measurements do not disagree.

@@

The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
to the free proton. The measurements disagree with the off-shell \cite{simonetta_2} and the on-shell calculations that use the medium modified GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}.
%the enhancement predicted by the on-shell calculations that use the medium modified GPDs as calculated from the quark-meson coupling model \cite{Guzey:2008fe}. The off-shell calculations overshoot the data indicating a trend \cite{simonetta_2}. 
In particular, the anti-shadowing region where off-shell model expects enhancement of the ratio experiment shows a sharp drop. Within the given 
uncertainties, our measured ratios are compatible with the previously measured 
single point from HERMES \cite{Airapetian}.

%These data, while limited in statistics, proved the experimental feasibility of measuring DVCS of bound-nucleons in addition to the EMC effect within the GPDs framework and led the way to the approval of a next generation nuclear measurements \cite{Armstrong:2017wfw}. The future measurements will be carried out using the new CLAS12 spectrometer and the upgraded CEBAF 12 GeV electron beam at an electron-nucleon luminosity of 10$^{35}$cm$^{-2}$s$^{-1}$. The wider accessible phase-space and the higher luminosity will enable us to study nuclear effects and their manifestations on GPDs including the effect of final state interactions.

%conclusion
In summary, we have presented the first exclusive beam-spin asymmetry measurements 
associated with incoherent DVCS off $^4$He using an upgraded setup of the CLAS 
spectrometer at Jefferson Lab. Our results were compared to model 
calculations based on different assumptions of the nuclear medium effects at 
the partonic level.
% and allowed us to draw some conclusions. 
The bound-proton 
beam-spin asymmetries indicate a suppression compared to the free proton 
results measured in similar phase-space. While the data are limited in 
statistics, they opened new avenue for future measurements. This study lead to the approval of a next generation nuclear 
DVCS measurements \cite{Armstrong:2017wfw} using the new CLAS12 spectrometer and the upgraded CEBAF 12 GeV electron 
beam.

>>>>

\begin{document}
\linenumbers

\title{First exclusive Deeply Virtual Compton Scattering measurement off bound nucleon in $^4$He}

@@

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurements in incoherent 
 deeply virtual Compton scattering (DVCS) off $^4$He using the fully exclusive 
 final state. The data were accumulated using a 6 GeV longitudinally polarized 
 electron beam incident on a pressurized $^4$He gaseous target placed in front 
 of the CLAS spectrometer in Hall-B at the Thomas Jefferson National 
 Accelerator Facility. The azimuthal angular ($\phi$) dependence of the BSA is 
 studied in a wide range of virtual photon and scattered proton 
 kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound nucleon has 
 been compared with the one on the free proton. In the whole kinematical region of our 
 measurements, the BSA on the bound nucleon is smaller by about $20\%$ to $30\%$, 
 indicating possible medium modification on the nucleon's partonic structure.  
 This measurement opens a new opportunity to explore the origin of the EMC 
 effect within the framework of the generalized parton distributions.

@@

Electromagnetic probes have played a major role in advancing our knowledge 
about the structure of the nucleon, which is at the origin of almost all the
universe's visible matter. While elastic lepton-nucleon measurements have 
taught us about the spatial charge and magnetization distributions 
\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering 
experiments have uncovered the features of momentum sharing between the 
constituents partons, i.e., quarks and gluons \cite{Dokshitzer:1977sg,pdg}.  
With nuclear targets, these measurements have revealed the fact that the 
distribution of quarks in a nucleus is not a simple convolution of 
their distributions within nucleons, an observation known as the ``EMC 
effect''\cite{EMC_first} (for reviews on the topic, see  
\cite{EMC_CERN,EMC_SLAC,EMC_HERMES,EMC_JLab,EMC_John,EMC_mdeium_1,EMC_medium_2}).

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations are set to be revealed through deeply virtual Compton scattering 
(DVCS), i.e., the hard exclusive lepto-production of a real photon, which 
provides access to a three-dimensional imaging of partons within the 
generalized parton distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. Combining these measurements has enabled the first extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of exclusive DVCS from the $^{4}$He nucleus are a critical 
step towards providing similar 3-D pictures of the quark structure of the 
nucleus as a whole, via the coherent channel 
\cite{Airapetian:2009cga,Hattawy:2017woc}, and provide a new approach for 
understanding modifications of the partonic structure of the bound nucleons via 
the incoherent DVCS channel \cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for these purposes as it is 
characterized by a strong binding energy, a relatively high nuclear 
core density, and a large EMC effect~\cite{JSeely}. However, it remains simple 
enough that exact calculation of its structure 
can be performed, making this nucleus the perfect target for our investigation of the 
medium modifications of the nucleon's partonic structure.

@@

In this Letter, we present the first exclusive measurement of the beam-spin asymmetry 
in deeply virtual electroproduction of a real photon off bound-proton in $^{4}$He. 
Experimentally, we measure the squared sum of the Bethe-Heitler (BH) and the DVCS 
amplitudes, with the BH process the process where the real photon is emitted by 
the incident or the scattered electron rather than the nucleon. The beam-spin 
asymmetry arises from the interference of these two terms and is directly 
sensitive to the DVCS amplitude that contain the information on the GPDs. 
Using a longitudinally polarized electron beam (L) and an unpolarized target 
(U), this beam-spin asymmetry observable is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the 
beam-spin asymmetry can be simplified as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)}
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the above mentioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ 
and is proportional to the following combination of Compton form factors (CFF) 
\cite{Guidal:2013rya}
\begin{equation}
   A_{LU}^{\sin\phi} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} 
   F_2 \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}})
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors and $x_B$ the 
Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  
\begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi) \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, there $\xi$ is the 
skewing factor and can be
related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$. Similar expressions apply 
for the GPDs $E$, $\widetilde{H}$, and $\widetilde{E}$.

@@

The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
(CEBAF) accelerator at energy of 6.064 GeV. The data were accumulated 
over 40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous 
$^4$He target centered at 64~cm upstream of the CEBAF Large Acceptance 
Spectrometer (CLAS) coordinate center. For DVCS experiments, the CLAS baseline 
design \cite{Mecking:2003zu} 
is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC extends 
the photon detection acceptance of CLAS to very small polar angles, 4$^{\circ}$. 
The 5-Tesla solenoid magnet in the center of which the target was located 
prevented the high-rate low-energy M{\o}ller electrons from reaching the CLAS 
drift chambers by guiding these electrons inside a tungsten shield placed around the beam line.

% DVCS selection
Incoherent DVCS events were selected if an electron, a proton, and at least one 
photon were detected in the final state. Electrons were identified as negatively 
charged tracks reconstructed in drift chambers with an appropriate energy 
deposition in the electromagnetic calorimeter (EC) and a proper light yield in 
the Cherenkov counters. The protons were identified from positively charged tracks by 
timing analysis using the time-of-flight measured by the scintillator counters. 
In addition, it was required that both the electron and the proton in the event 
originated from the same vertex at the target within CLAS tracking vertex 
resolution. The photons were detected in either the IC or 
the CLAS electromagnetic calorimeter. All the clusters within the IC fiducial region 
were assumed to be photons, while a timing cut is used to clean the EC photons 
from neutrons. Note that even though the DVCS reaction has only one real photon 
in the final state, events with more than one photon were not discarded at 
this stage. These are mostly soft photons from accidental coincidence which, 
as will be discussed below, the DVCS exclusivity cuts eliminate easily. In the 
following selection stage, the most energetic photon is considered as the DVCS 
photon candidate (see \cite{Hattawy:thesis} for additional details on the 
particles identification).

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
events due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. For the accidental events, i.e., $e'p'\gamma$ collection 
with particles originated from different electron scattering events, their contribution 
was evaluated to be of 6.5\% by selecting events passing all our cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using the data and 
simulation. From simulation, we calculated the ratio ($R$) of the number of $\pi^0$ 
events that are identified as $ep\rightarrow e'p'\gamma$ events after our selection 
cuts to the number of identified $\pi^0$ events, 
$R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ is the 
experimentally identified number of $ep\rightarrow e'p'\gamma$ and 
$N^{ep\rightarrow e'p'\pi^0}_{exp}$ is the experimentally identified 
$ep\rightarrow e'p'\pi^0$ with the two photons detected. Depending on the 
kinematics, we found this contamination to be of 8\% to 10\%.

%asymmetries
Experimentally, $A_{LU}$ is defined as
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} }.
\end{equation}
where $N^{+}$ and $N^{-}$ are the number of DVCS events for positive and negative 
beam-helicity state, and $P_{B}$ is the longitudinal beam polarization.

In the kinematical domain of our experiment, the dominant contribution to the 
beam-spin asymmetry comes from the GPD $H$ \cite{Guidal:2013rya} as the $\phi$ 
dependence of $A_{LU}$ gives access to the real and imaginary part of the CFF 
$\mathcal{H}$ through the parameters $a_0$, $a_1$, and $a_2$ of equation \ref{eq:alu-simp}. The studies of  
the free proton $A_{LU}$ measurements, \cite{Girod:2007aa}, have 
shown that the the pure DVCS contribution, $cos(2\phi)$ term ($a_2$), is suppressed and compatible with zero.  
{\bf Raphael: This paragraph is very confusing, is it true that a1 and a2 are 
dominated by H? Do we have equivalents of eq. 3 for those? I actually did not find
it in ref 31, which we are referring and we are also not using the same definition
of Im(H)...}

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four statistically-equivalent bins in one of the kinematical 
variable of interest -- $Q^{2}$, $x_{B}$ or $t$ -- were constructed, then each 
bin is divided into nine bins in the azimuthal angle ($\phi$).  
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
of the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The main contributions 
to systematic uncertainties on these fits are from the choice of the DVCS 
exclusivity cuts (6\%) and the large binning size (7\%). Added quadratically, 
these uncertainties sum up to less than 10\% for all data points and remain 
significantly smaller than the statistical errors.

\begin{figure}[tb]
\includegraphics[width=8.9cm]{figs/incoherent_ALU_phi.pdf}
\caption{The incoherent $A_{LU}$ as a function of $\phi$. Results are presented
   for different $Q^{2}$ bins (top panel), $x_{B}$ bins (middle panel), and 
   $-t$ bins (bottom panel). The error bars represent the statistical 
   uncertainties. The gray bands represent the systematic uncertainties, 
   including the normalization uncertainties. The black curves are the results 
   of our fits with the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$.}
\label{fig:alu}
\end{figure}

We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
signals at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model uses a realistic spectral function and 
considers off-shell effects. The calculations are carried out at slightly 
different kinematics than our data but still provide important guidance. The 
experimental results appear to have smaller asymmetries than the calculations.  
These differences may arise from nuclear effects which are not taken into 
account in the model, such as long-range interactions. On the graph for $-t$ 
dependence, we show previous measurements by the HERMES collaboration
\cite{Airapetian:2009cga} using inclusive final state, ($e^\prime\gamma$). Due 
to large experimental uncertainties of HERMES points, the two measurements 
do not disagree, but we can also see that their high $-t$ results were 
smaller than expected by models.

@@

The $A_{LU}$ ratios show a 20\%-40\% lower asymmetries for a bound proton compared 
to the free proton. The measurements disagree with the off-shell \cite{simonetta_2} 
and the on-shell calculations that use the medium modified GPDs as calculated from 
the quark-meson coupling model \cite{Guzey:2008fe}. In particular, at lower $x_B$, 
where the off-shell model predicts an enhancement of the ratio, our experiment 
shows a sharp drop. This measurement shows that an important nuclear effect is
missing from the existing models in order to explain this strong quenching of
the beam-spin asymmetry.

%conclusion
In summary, we have presented the first exclusive beam-spin asymmetry measurements 
associated with incoherent DVCS off $^4$He using an upgraded setup of the CLAS 
spectrometer at Jefferson Lab. Our results were compared to model 
calculations based on different assumptions of the nuclear medium effects at 
the partonic level.  The bound-proton 
beam-spin asymmetries is largely suppressed compared to the free proton 
results measured in a similar phase-space. This surprising result opens a new avenue 
for progress in the understanding of the quarks and gluons behavior in the
nuclear medium.
